Modelling the gas kinematics of an atypical Lyman alpha emitting compact dwarf galaxy

### 2017-06-18 paper/paper.tex
small issues solved

@@

Why is it that the other parameters do not seem to matter? Probably
because $P_{cl}$ (the probability for a \lya\ to be emitted in a
clump) is high and most photons are produced at
large radii making the radiative transfer effects in the center less
important.  
We cannot discard that another region of parameter space with similar
velocity structure but an empty inter-clump medium, relatively dense
clumps and at least a few clumps per sightline 
could also work \citep{Hansen06}.
This possibility does not change our conclusions about the
kinematic parameters, but it might be interesting to explore in the
future with a higher sampling of the parameter space once new
observations clarify the kinematic nature of \tol.

@@

Lower rotational velocities are disfavored by the fact that the line
is single peaked.
Fixing the optical depth at a high value of $10^7$ ensures that the line width
is close to its observed value.
A lower rotational velocity would produce a double peaked line.
The fact that the velocity and optical depth priors were wide enough,
allows us to think that the current values found by the MCMC are
robust given the observational constraints.

@@

\tol\ shows one of the most atypical \lya\ spectra observed so far.
Its flux at the line's center is high compared to other LAEs at low
redshift and the wide symmetrical peak is virtually absent from other
LAEs at low and high redshift \citep{LARS,Erb14,Trainor16}. Simple
shell models fail to reproduce such a spectrum
\cite{2015A&A...578A...7V}.  
In the previous sections we show how these characteristics can be
explained by rather extreme kinematic characteristics.
Now we discuss and frame those results in terms of the dynamical mass
that could explain the velocities obtained in the model.

@@

A new observational test is needed to clarify the kinematic nature of
\tol. 
We suggest that integral field unit measurements 
resolving its spatial extent are up to the task. 
\tol\ spans a region of $4$ arcseconds,
an instrument such as the Multi Unit Spectroscopic Explorer (MUSE)
\citep{2014Msngr.157...13B} with its
nominal $0.2$ arcseconds spatial sampling over a $1.0$ arcminute field
in wide-field mode could provide a coarse mapping of different
ionization lines to infer a kinematic map in the H$\alpha$ line,
following the kind of work presented by \citet{Herenz16} done with the Potsdam
Multi-Aperture Spectrometer (PMAS) \citet{PMAS} on nearby
\lya\ emitting galaxies.
We note that archival Chandra X-ray archival
data \footnote{\url{http://cxc.harvard.edu/cda/}} does not show any
detection for \tol.
This lack of detection would also put an upper limit on the intensity
of recent black hole activity due to accretion.

@@

\section{Conclusions}

>>>>

Archival Chandra X-ray data \footnote{\url{http://cxc.harvard.edu/cda/}} does not show any
detection for \tol. 
This lack of detection motivates our assumption that \lya\ emission is
powered by star formation only.

@@

Why is it that the other parameters do not seem to matter? Probably
because $P_{cl}$ (the probability for a \lya\ to be emitted in a
clump) is high and most photons are produced at
large radii making the radiative transfer effects in the center less
important.  
We cannot discard that another region of parameter space with similar
velocity structure but an empty inter-clump medium, relatively dense
clumps and at least a few clumps per sightline 
could also work \citep{Hansen06}.
This possibility does not change our conclusions about the
kinematic parameters, but it might be interesting to explore in the
future with a higher sampling of the parameter space once new 
observations  clarify the kinematic nature of \tol \footnote{In Section \S \ref{sec:conclusions} we describe  in more detail what kind of observations could be performed in the
  near future to improve our understanding of \tol's kinematics.} .

@@

Lower rotational velocities are disfavored by the fact that the line
is single peaked.
The observed line width is better reproduced with a
high optical depth value $\sim10^7$ as we found.
For such optical depth values a lower rotational velocity would
produce a double peaked line \citep{GaravitoCamargo2014}. 
The fact that the velocity and optical depth priors were wide enough,
allows us to suggest that the current values found by the MCMC are
robust given the observational constraints.

@@

\tol\ shows one of the most atypical \lya\ spectra observed so far.
Its flux at the line's center is high compared to other LAEs at low
redshift and the wide symmetrical peak is virtually absent from other
LAEs at low and high redshift \citep{2012ApJ...751...29Y,LARS,Erb14,Trainor16}. Simple
shell models fail to reproduce such a spectrum
\cite{2015A&A...578A...7V}.  
In the previous sections we show how these characteristics can be
explained by rather extreme kinematic characteristics.
Now we discuss and frame those results in terms of the dynamical mass
that could explain the velocities obtained in the model.

@@

A new observational test is needed to clarify the kinematic nature of
\tol. 
We suggest that integral field unit measurements 
resolving its spatial extent are up to the task. 
\tol\ spans a region of $4$ arcseconds,
an instrument such as the Multi Unit Spectroscopic Explorer (MUSE)
\citep{2014Msngr.157...13B} with its
nominal $0.2$ arcseconds spatial sampling over a $1.0$ arcminute field
in wide-field mode could provide a coarse mapping of different
ionization lines to infer a kinematic map in the H$\alpha$ line,
following the kind of work presented by \citet{Herenz16} done with the Potsdam
Multi-Aperture Spectrometer (PMAS) \citet{PMAS} on nearby
\lya\ emitting galaxies.

@@

\section{Conclusions}
\label{sec:conclusions}
